Downward shortwave solar irradiance enhancement by clouds.

### 2024-05-21 article/article.tex
Commit 2024-05-21 18:10

The use of the actual modeled values of clear sky GHI, described above ,
can not provide us with a robust method to distinguish the CE cases, due
to the limited accuracy of the input data. Our main focus was to
positively identify over irradiance events from CEs, so we created an
upper envelope of the clear sky irradiance,

\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots\ldots..

above which, any GHI value can safely attributed to CE. We evaluated the
performance of the modeled clear radiation for each of atmospheric level
of clearness, as reference, in order to conclude which is the most
appropriate.

>>>>

The use of the actual modelled values of clear sky GHI, described above,
can not provide us with a robust method to distinguish the CE cases, due
to the limited accuracy of the input data, and the natural variability
of the atmosphere. Our main focus was to positively identify over
irradiance events related to CEs. For this reason, we created an upper
envelope of the clear sky irradiance, above which, any GHI value can
safely be attributed to CE a event.

We had to select both, an appropriate set of atmospheric
parameterization, in Libradtran, and the thresholds of CE
identification. First we evaluated the performance of the modelled clear
radiation, for each of atmospheric level of clearness we have created as
reference, in order to conclude which is the most appropriate.
